Verifying Demonstrations

### 2021-06-16 paper/protest-model.tex

\begin{definition}[Valid proof share]%
  \label{DefProofShare}\label{DefProofShares}
  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\);
  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).

  Furthermore, we say that \(\psh\) is \emph{valid} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).
  We let \(\pshs\) denote the set of all proof shares and \(
    \pshs_\prtst = \{ \psh \in \pshs \mid
      \exists \sprtst \in \prtst, \psh \sqsubseteq \sprtst \}
  \) be the subset of valid proof shares related to a protest~\(\prtst\).
\end{definition}

We denote by \(=_\pid\) the equivalence relation on \(\pshs\) where \((\cid, t, 
l, \pid, \wid) =_\pid (\cid', t', l', \pid', \wid')\) if \(\pid = \pid'\).
%and we will use the following notation to filter out a subset of \(\pshs\) with 
%specific \(\cid\)s and \(\pid\)s:
%\begin{multline*}
%  \pshs_{\cid_0, \pid_0} = \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = 
%  \cid_0 \land \pid = \pid_0\}.
%\end{multline*}

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  We denote by \(\prfs_\prtst = \pshs_\prtst/{=_\pid}\) the \emph{set of all 
  proofs of participation for the protest~\(\prtst\)}.
  The \emph{participation proof} of a protester with pseudonym~\(i\) who 
  participates in a protest~\(\prtst\) is the set
  \begin{equation}
    \nonumber
    \prf_{i, \prtst} =
    \left\{ (\cid, t, l, \pid, \wid) \in \pshs_\prtst \mid
      \pid = i\right\},
  \end{equation}
  of all proof shares with the same protester and valid for any subprotest of 
  \(\prtst\).
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]%
  \label{DefParticipationCount}
  We define a \emph{participation count} of a protest \(\prtst\) as the cardinality 
  \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{eligible} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs_\prtst
      \mid
      \str(\prf_{i,\prtst})\geq \theta \right\}
  \] with \(\str\colon \powerset(\pshs)\to \RR_+\) and  \(\theta \in \RR_+\).
\end{definition}

>>>>

\begin{definition}[Valid proof share]%
  \label{DefProofShare}\label{DefProofShares}\label{ValidProofShare}
  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\);
  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).

  Furthermore, we say that \(\psh\) is \emph{valid} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).
  We let \(\pshs\) denote the set of all proof shares and \(
    \pshs_{\prtst} = \{ \psh \in \pshs \mid
      \exists \sprtst \in \prtst, \psh \sqsubseteq \sprtst \}
  \) be the subset of valid proof shares related to a protest~\(\prtst\).
\end{definition}

We denote by \(=_{\pid}\) the equivalence relation on \(\pshs\) where \((\cid, 
t, l, \pid, \wid) =_{\pid} (\cid', t', l', \pid', \wid')\) if \(\pid = \pid'\).
%and we will use the following notation to filter out a subset of \(\pshs\) with 
%specific \(\cid\)s and \(\pid\)s:
%\begin{multline*}
%  \pshs_{\cid_0, \pid_0} = \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = 
%  \cid_0 \land \pid = \pid_0\}.
%\end{multline*}

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  We denote by \(\prfs_{\prtst} = \pshs_{\prtst}/{=_{\pid}}\) the \emph{set of 
  all proofs of participation for the protest~\(\prtst\)}.
  The \emph{participation proof} of a protester with pseudonym~\(i\) who 
  participates in a protest~\(\prtst\) is the set
  \begin{equation}
    \nonumber
    \prf_{i, \prtst} =
    \left\{ (\cid, t, l, \pid, \wid) \in \pshs_{\prtst} \mid
      \pid = i\right\},
  \end{equation}
  of all proof shares with the same protester and valid for any subprotest of 
  \(\prtst\).
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]%
  \label{DefParticipationCount}
  We define a \emph{participation count} of a protest \(\prtst\) as the cardinality 
  \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{eligible} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs_{\prtst}
      \mid
      \str(\prf_{i,\prtst})\geq \theta \right\}
  \] with \(\str\colon \powerset(\pshs)\to \RR_+\) and  \(\theta \in \RR_+\).
\end{definition}

### 2021-06-16 paper/security-properties.tex
Clarifies security properties (relates them to protest model)

    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.

    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.

@@

    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof 
      is designated for the particular protest.

@@

What these properties say is that pseudonyms must look random 
(\cref{PseudonymUnlink}) and that each psdeudonym must not be reused
more than strictly necessary for the verifiability properties 
(\cref{ProtestUnlink,WitnessUnlink}). In Pfitzmann-Hansen
terminology~\cite{pfitzmann-hansen}, they are role-relationship
pseudonyms, but with increasingly narrowed notions of roles and
relationships (participant of particular protest, witness of a
particular participant at a particular protest).
In the terminology of \textcite{SybilFreePseudonyms}, for each protester a 
protest is a context or identity domain whereas for each witness every 
protester is a context (or identity domain).

>>>>

    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
      \Ie \(t\subseteq t_\prtst\) in \cref{ValidProofShare}.

    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
      \Ie \(l\subseteq l_\prtst\) in \cref{ValidProofShare}.

@@

    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof 
      is designated for the particular protest.
      \Ie designated to \(\cid\) in \cref{ValidProofShare}.

@@

What these properties say is that pseudonyms must look random 
(\cref{PseudonymUnlink}) and that each psdeudonym must not be reused
more than strictly necessary for the verifiability properties 
(\cref{ProtestUnlink,WitnessUnlink}). In Pfitzmann-Hansen
terminology~\cite{pfitzmann-hansen}, they are role-relationship
pseudonyms, but with increasingly narrowed notions of roles and
relationships (participant of particular protest, witness of a
particular participant at a particular protest).
In the terminology of \textcite{SybilFreePseudonyms}; for each protester a 
protest is a context or identity domain, whereas for each witness every 
protester is a context (or identity domain).
